---
title: "Introduction to linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4)
```

## Fitting a model

`linreg` fits a multiple linear regression model using the QR
decomposition. The model is created with a formula and a data set, in the
same way as `lm()`:

```{r}
mod <- linreg$new(Petal.Length ~ Sepal.Width + Sepal.Length, data = iris)
mod
```

## Coefficients

The estimated coefficients are available with `coef()`:

```{r}
mod$coef()
```

## Fitted values and residuals

The fitted values and residuals are available with `pred()` and `resid()`:

```{r}
head(mod$pred())
head(mod$resid())
```

## Summary

`summary()` prints the coefficients together with their standard errors,
t-values and p-values, as well as the residual standard error and the
degrees of freedom:

```{r}
mod$summary()
```

## Diagnostic plots

`plot()` produces a residuals vs fitted plot and a scale-location plot:

```{r, fig.width = 6, fig.height = 4}
mod$plot()
```
